Manuscript

### 2015-03-14 inst/simulation/manuscript.Rmd
...

getLogPopulationSizes <- function(populationSizes) {
  logPopulationSizes <- populationSizes
  logPopulationSizes$Observed <- log10(logPopulationSizes$Observed + 1)
  logPopulationSizes$Estimated <- log10(logPopulationSizes$Estimated + 1)
  return(logPopulationSizes)
}
```

```{r figure-3-init-2}
populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames[c(1,3,4,5)])
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,4,5)])
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,4,5)])

@@

```{r figure-4abc}
pc1 <- getPopulationCorrelations(scenarios=scenarios, modelNames=modelNames[1], cutoff=cutoff)
pc2 <- getPopulationCorrelations(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[1], cutoff=cutoff)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)

@@

```{r figure-5-init}
getCIProportions <- function(scenarios, modelNames, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenarios, modelNames=modelNames, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) +
    scale_colour_manual("Model", values=c("black", "gray26", "gray80"), labels=modelLabels) +
    #scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"))
  return(p)
}
#p <- plotCIProportions(cip)
#saveFigure(p, "manuscript-figure-5.png", height=7.87/2, dpi=200)
```

```{r figure-5abc}
cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[c(1,3,5)], panel="Case 1", scenarioNames=scenarios, cutoff=cutoff)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,5)], panel="Case 2", scenarioNames=scenarios, cutoff=10*cutoff)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,5)], panel="Case 3", scenarioNames=scenarios, cutoff=cutoff)

>>>>

getLogPopulationSizes <- function(populationSizes) {
  logPopulationSizes <- populationSizes
  logPopulationSizes$Observed <- log10(logPopulationSizes$Observed + 1)
  logPopulationSizes$Estimated <- log10(logPopulationSizes$Estimated + 1)
  return(logPopulationSizes)
}

populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames[c(1,3,4,5)])
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,4,5)])
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,4,5)])

@@

```{r figure-4abc}
pc1 <- getPopulationCorrelations(scenarios=scenarios, modelNames=modelNames[1], cutoff=cutoff)
pc2a <- getPopulationCorrelations(scenarios="Acombined", modelNames=modelNames[1], cutoff=cutoff)
pc2b <- getPopulationCorrelations(scenarios="Bcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2c <- getPopulationCorrelations(scenarios="Ccombined", modelNames=modelNames[1], cutoff=cutoff)
pc2d <- getPopulationCorrelations(scenarios="Dcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2e <- getPopulationCorrelations(scenarios="Ecombined", modelNames=modelNames[1], cutoff=cutoff)
pc2f <- getPopulationCorrelations(scenarios="Fcombined", modelNames=modelNames[1], cutoff=cutoff)
pc2 <- rbind(pc2a,pc2b,pc2c,pc2d,pc2e,pc2f)
pc3 <- getPopulationCorrelations(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[1], cutoff=cutoff)

@@

```{r figure-5}
getCIProportions <- function(scenario, modelName, panel, scenarioNames, cutoff=Inf) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study, populationSizeCutoff=cutoff)
  a <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenario, modelNames=modelName)
  b <- validation$getValidatedCredibilityIntervalsProportions(scenarios=scenario, modelNames=modelName, probs=c(.25, .75), probsName="50%")
  credibilityIntervals <- rbind(a, b)
  credibilityIntervals$panel <- panel
  credibilityIntervals$scenario <- rep(scenarioNames, times=2, each=length(modelNames))
  return(credibilityIntervals)  
}

plotCIProportions <- function(credibilityIntervals) {
  modelLabels <- prettyModelName(unique(credibilityIntervals$modelName))
  credibilityIntervals$CI <- credibilityIntervals$Interval
  p <- ggplot(credibilityIntervals, aes(scenario, Proportion, shape=CI, colour=modelName)) +
    geom_hline(aes(yintercept=.5), color="grey90") +
    geom_hline(aes(yintercept=.95), color="grey90") +
    geom_point() +
    scale_shape_manual(values=c(16, 1)) +
    scale_colour_manual("Model", values=c("black", "gray26", "gray80"), labels=modelLabels) +
    #scale_colour_manual("Model", values=c("blue", "green", "red"), labels=modelLabels) +
    theme_minimal(base_size=10) + theme(panel.border=element_rect(fill="transparent")) +
    xlab("Scenario") + ylab("Proportion") +
    facet_wrap(~panel) + ylim(0, 1) +
    theme(panel.grid.major=element_blank(), panel.grid.minor=element_blank(),
          plot.margin=unit(c(0.2, 0, 0, 0), units="line"),
          #legend.background=element_rect(fill="transparent"),
          legend.margin=unit(-2, units="line"),
          panel.margin=unit(0, units="line"),
          legend.position="bottom",
          legend.box="horizontal",
          legend.key.width=unit(.7, "line"))
  return(p)
}
#p <- plotCIProportions(cip)
#saveFigure(p, "manuscript-figure-5.png", height=7.87/2, dpi=200)

cip1 <- getCIProportions(scenarios=scenarios, modelNames=modelNames[c(1,3,5)], panel="Case 1", scenarioNames=scenarios, cutoff=cutoff)
cip2 <- getCIProportions(scenarios=paste0(scenarios, "combined"), modelNames=modelNames[c(1,3,5)], panel="Case 2", scenarioNames=scenarios, cutoff=10*cutoff)
cip3 <- getCIProportions(scenarios=paste0(scenarios, "10days"), modelNames=modelNames[c(1,3,5)], panel="Case 3", scenarioNames=scenarios, cutoff=cutoff)
